---
title: 'RStudio: Number Theory'
output:
  pdf_document: default
  html_document:
    includes:
      after_body:
      - include_lessons_nav_end.html
      - include_footer.html
      before_body:
      - include_header.html
      - include_rstudio_nav.html
  
---
### **Numbers Package**

The numbers package provides number-theoretic functions for factorization, prime numbers, twin primes, primitive roots, modular logarithm and inverses, extended GCD, Farey series and continuous fractions. It includes Legendre and Jacobi symbols, some divisor functions, Euler's Phi function, etc.
To load the package type
```{r}
library(numbers)
```


### **Divisors Function**

divisors($n$) Generates a list of divisors of an integer number ($n$). The list of all divisors of an integer $n$ will be calculated and returned in ascending order, including 1 and the number itself. For $n\geq 1000$ the list of prime factors of n will be used, for smaller $n$ a total search is applied.

Divisors of 6
```{r}
divisors(6)
```

Divisors of 10
```{r}
divisors(10)
```

Divisors of 12
```{r}
divisors(12)
```

Divisors of 60
```{r}
divisors(60)
```


### **GCD and LCM Integer Functions**

The functions generate the greatest common divisor and least common multiple of integers. Computation is based on the Euclidean algorithm.

greatest common divisor of 341 and 527
```{r}
GCD(341,527)
```

least common multiple of 341 and 527
```{r}
LCM(341,527)
```

### **Prime Factors Function**

Computes a vector containing the prime factors of an integer $n$.

Prime factors of 88
```{r}
primeFactors(88)
```


***
Trevor. N. Mutusva, February 2020.

